Considering scale in multilayer animal social networks

### 2020-08-26 paper/manuscript.Rmd
portable affiliations in yaml
thanks to this SO question: https://stackoverflow.com/questions/52918716/authors-and-affiliations-in-the-yaml-of-rmarkdown
and @tarleb

---
title: Considering scale in multilayer animal social networks
author: Alec L. Robitaille^1\*^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
date: |
  | ^1^Department of Biology, Memorial University of Newfoundland, Canada
  | ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland 
  | \*Corresponding author: Alec L. Robitaille (robit.alec@gmail.com)
output:
   # bookdown::github_document2: default
   bookdown::word_document2:
     reference_docx: template.docx
knit: (function(inputFile, encoding) {
  rmarkdown::render(input = inputFile, encoding = encoding, output_format = "all") })
bibliography: ../references/knitcite.bib
csl: csl.csl
---

>>>>

---
title: Considering scale in multilayer animal social networks
author:
  - name: Alec L. Robitaille
    email: robit.alec@gmail.com
    institute: bio
    correspondence: true
  - name: Quinn M.R. Webber
    institute: cabe
  - name: Julie W. Turner
    institute: bio
  - name: Eric Vander Wal
    institute: [bio, cabe]
institute: 
  - bio: Department of Biology, Memorial University of Newfoundland, Canada
  - cabe: Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland 
output:
   bookdown::word_document2:
     reference_docx: template.docx
     pandoc_args:
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
knit: (function(inputFile, encoding) {
  rmarkdown::render(input = inputFile, encoding = encoding, output_format = "all") })
bibliography: ../references/knitcite.bib
csl: csl.csl
---
